\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2022-11-30 doc/USER_MANUAL/04_creating_databases.tex

When that option is on, of course the number of processor cores used to start
the code in the batch system must be a multiple of \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS},
all the individual runs must use the same number of processor cores,
which as usual is NPROC in the \texttt{DATA/Par\_file},
and thus the total number of processor cores to request from the batch system
should be \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS}~*~\texttt{NPROC}.
All the runs to perform must be placed in directories called run0001, run0002, run0003 and so on
(with exactly four digits).

Imagine you have 10 independent calculations to do, each of them on 100 cores; you have three options:

1/ submit 10 jobs to the batch system

2/ submit a single job on 1000 cores to the batch, and in that script create a sub-array of jobs to start 10 jobs,
each running on 100 cores (see e.g. \url{http://www.schedmd.com/slurmdocs/job_array.html})

3/ submit a single job on 1000 cores to the batch, start SPECFEM3D on 1000 cores, create 10 sub-communicators,
cd into one of 10 subdirectories (called e.g. run0001, run0002,... run0010) depending on the sub-communicator
your MPI rank belongs to, and run normally on 100 cores using that sub-communicator.

The option \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS} implements 3/.

\item [{\texttt{BROADCAST\_SAME\_MESH\_AND\_MODEL}}] if we perform simultaneous runs in parallel,
if only the source and receivers vary between these runs
but not the mesh nor the model (velocity and density) then we can also read the mesh and model files
from a single run in the beginning and broadcast them to all the others; for a large number of simultaneous
runs for instance when solving inverse problems iteratively this can DRASTICALLY reduce I/Os to disk in the solver
(by a factor equal to \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS}), and reducing I/Os is crucial in the case of huge runs.
Thus, always set this option to .true. if the mesh and the model are the same for all simultaneous runs.
In that case there is no need to duplicate the mesh and model file database (the content of the DATABASES\_MPI
directories) in each of the run0001, run0002,... directories, it is sufficient to have one in run0001
and the code will broadcast it to the others).

@@

TODO / future work to do: currently the \texttt{BROADCAST\_SAME\_MESH\_AND\_MODEL}
option assumes to have the (main) mesh files in \texttt{run0001/DATABASES\_MPI} or
\texttt{run0001/OUTPUT\_FILES/DATABASES\_MPI}.
However, for adjoint runs you still need a \texttt{DATABASES\_MPI/} folder in each of the sub-runs directories,
e.g. \texttt{run0002/DATABASES\_MPI}, etc. to store the forward wavefields, kernels etc. of each sub-run.
This would not be needed for forward simulations.

TODO / future work to do: the sensitivity kernel summing and smoothing tools in directory src/tomography are currently not ported to this new option to do many runs simultaneously, only the solver (src/specfem3d) is. Thus these tools should work, but in their current version will need to be run for each simulation result independently.

More precisely, the current kernel summing and smoothing routines work fine, with the exception that you need to move out the mesh files (and also the parameters). This works because these routines consider multiple runs by design. You simply have to provide them the directories where the kernels are.

@@

If you use PML, the mesh elements that belong to the PML layers can
be acoustic or elastic, but not viscoelastic nor poroelastic. Then,
when defining your model, you should define these absorbing elements
as either acoustic or elastic. In you forget to do that, the code
will fix the problem by automatically converting the viscoelastic
or poroelastic PML elements to elastic. This means that strictly speaking
the PML layer will not be perfectly matched any more, since the physical
model will change from viscoelastic or poroelastic to elastic at the
entrance of the PML, but in practice this is sufficient and produces
only tiny / negligible spurious reflections.

If you use PML and an external mesh (created using an external meshing tool
such as CUBIT/TRELIS or similar), try to have elements inside the PML as regular as possible,
i.e. ideally non-deformed cubes obtained by `extrusion' of regular surface mesh elements meshing the
outer edges of the computational domain without PML; by doing so, the PMLs obtained will be far more stable
in time (PML being weakly unstable from a mathematical point of view, very deformed mesh elements
inside the PMLs can trigger instabilities much more quickly). \red{We have two utilities in directory utils/CPML that do that automatically
and that are very fast}. To stabilize PMLs it also helps to add a transition layer of geometrically-regular non-PML elements, in which attenuation is also
turned off (i.e. $Q_\kappa = Q_\mu = 9999$ in that layer), as in the red layer of Figure~\ref{fig:mesh_extrusion}.
Our tools in directory utils/CPML implement that transition layer automatically.

If you use PML and an external tomographic velocity and density model,
you should be careful because mathematically a PML cannot handle heterogeneities
along the normal to the PML edge inside the PML layer. This comes
from the fact that the damping profile that is defined assumes a constant
velocity and density model along the normal direction.
Thus, you need to modify your velocity and density model in order
for it to be 1D inside the PML, as shown in Figure~\ref{fig:modify_external_velocity_model_to_use_PML}.
This applies to the bottom layer as well; there you should make sure
that your model is 1D and thus constant along the vertical direction.

To summarize, only use a 3D velocity and density model inside the
physical region, and in all the PML layers extend it by continuity
from its values along the inner PML edge.

@@

The parameter \texttt{DT} sets the length of each time step in seconds.
The value of this parameter is crucial for the stability of the spectral-element
simulation. Your time step \texttt{DT} will depend on the minimum
ratio between the distance $h$ of neighboring mesh points and the
wave speeds $v$ defined in your model. The condition for the time
step $\Delta t$ is:
\begin{lyxcode}
$\Delta t<C~\mathrm{min}_{\Omega}(~h/v~)$
\end{lyxcode}
where $C$ is the so-called Courant number and $\Omega$ denotes the
model volume. The distance $h$ depends on the mesh element size and
the number of GLL points \texttt{NGLL} specified in the main constants
file \texttt{setup/constants.h}. The wave speed $v$ is determined based on your model's P- (or S-)
wave speed values.

>>>>

When that option is on, of course the number of processor cores used to start
the code in the batch system must be a multiple of \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS},
all the individual runs must use the same number of processor cores,
which as usual is NPROC in the \texttt{DATA/Par\_file},
and thus the total number of processor cores to request from the batch system
should be \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS}~*~\texttt{NPROC}.
All the runs to perform must be placed in directories called run0001, run0002, run0003 and so on
(with exactly four digits).\newline

Imagine you have 10 independent calculations to do, each of them on 100 cores; you have three options:\newline

1/ submit 10 jobs to the batch system\newline

2/ submit a single job on 1000 cores to the batch, and in that script create a sub-array of jobs to start 10 jobs,
each running on 100 cores (see e.g. \url{http://www.schedmd.com/slurmdocs/job_array.html})\newline

3/ submit a single job on 1000 cores to the batch, start SPECFEM3D on 1000 cores, create 10 sub-communicators,
cd into one of 10 subdirectories (called e.g. run0001, run0002,... run0010) depending on the sub-communicator
your MPI rank belongs to, and run normally on 100 cores using that sub-communicator.\newline

The option \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS} implements 3/.\newline

\item [{\texttt{BROADCAST\_SAME\_MESH\_AND\_MODEL}}] if we perform simultaneous runs in parallel,
if only the source and receivers vary between these runs
but not the mesh nor the model (velocity and density) then we can also read the mesh and model files
from a single run in the beginning and broadcast them to all the others; for a large number of simultaneous
runs for instance when solving inverse problems iteratively this can DRASTICALLY reduce I/Os to disk in the solver
(by a factor equal to \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS}), and reducing I/Os is crucial in the case of huge runs.
Thus, always set this option to .true. if the mesh and the model are the same for all simultaneous runs.
In that case there is no need to duplicate the mesh and model file database (the content of the DATABASES\_MPI
directories) in each of the run0001, run0002,... directories, it is sufficient to have one in run0001
and the code will broadcast it to the others).\newline

@@

TODO / future work to do: currently the \texttt{BROADCAST\_SAME\_MESH\_AND\_MODEL}
option assumes to have the (main) mesh files in \texttt{run0001/DATABASES\_MPI} or
\texttt{run0001/OUTPUT\_FILES/DATABASES\_MPI}.
However, for adjoint runs you still need a \texttt{DATABASES\_MPI/} folder in each of the sub-runs directories,
e.g. \texttt{run0002/DATABASES\_MPI}, etc. to store the forward wavefields, kernels etc. of each sub-run.
This would not be needed for forward simulations.\newline

TODO / future work to do: the sensitivity kernel summing and smoothing tools in directory src/tomography are currently not ported to this new option to do many runs simultaneously, only the solver (src/specfem3d) is. Thus these tools should work, but in their current version will need to be run for each simulation result independently.\newline

More precisely, the current kernel summing and smoothing routines work fine, with the exception that you need to move out the mesh files (and also the parameters). This works because these routines consider multiple runs by design. You simply have to provide them the directories where the kernels are.\newline

@@

If you use PML, the mesh elements that belong to the PML layers can
be acoustic or elastic, but not viscoelastic nor poroelastic. Then,
when defining your model, you should define these absorbing elements
as either acoustic or elastic. In you forget to do that, the code
will fix the problem by automatically converting the viscoelastic
or poroelastic PML elements to elastic. This means that strictly speaking
the PML layer will not be perfectly matched any more, since the physical
model will change from viscoelastic or poroelastic to elastic at the
entrance of the PML, but in practice this is sufficient and produces
only tiny / negligible spurious reflections.\newline

If you use PML and an external mesh (created using an external meshing tool
such as CUBIT/TRELIS or similar), try to have elements inside the PML as regular as possible,
i.e. ideally non-deformed cubes obtained by `extrusion' of regular surface mesh elements meshing the
outer edges of the computational domain without PML; by doing so, the PMLs obtained will be far more stable
in time (PML being weakly unstable from a mathematical point of view, very deformed mesh elements
inside the PMLs can trigger instabilities much more quickly). \red{We have two utilities in directory utils/CPML that do that automatically
and that are very fast}. To stabilize PMLs it also helps to add a transition layer of geometrically-regular non-PML elements, in which attenuation is also
turned off (i.e. $Q_\kappa = Q_\mu = 9999$ in that layer), as in the red layer of Figure~\ref{fig:mesh_extrusion}.
Our tools in directory utils/CPML implement that transition layer automatically.\newline

If you use PML and an external tomographic velocity and density model,
you should be careful because mathematically a PML cannot handle heterogeneities
along the normal to the PML edge inside the PML layer. This comes
from the fact that the damping profile that is defined assumes a constant
velocity and density model along the normal direction.
Thus, you need to modify your velocity and density model in order
for it to be 1D inside the PML, as shown in Figure~\ref{fig:modify_external_velocity_model_to_use_PML}.
This applies to the bottom layer as well; there you should make sure
that your model is 1D and thus constant along the vertical direction.\newline

To summarize, only use a 3D velocity and density model inside the
physical region, and in all the PML layers extend it by continuity
from its values along the inner PML edge.\newline

@@

The parameter \texttt{DT} sets the length of each time step in seconds.
The value of this parameter is crucial for the stability of the spectral-element
simulation. Your time step \texttt{DT} will depend on the minimum
ratio between the distance $h$ of neighboring mesh points and the
wave speeds $v$ defined in your model. The condition for the time
step $\Delta t$ is:
\begin{lyxcode}
$\Delta t<C~\mathrm{min}_{\Omega}(~h/v~)$
\end{lyxcode}
where $C$ is the so-called Courant number and $\Omega$ denotes the
model volume. The distance $h$ depends on the mesh element size and
the number of GLL points \texttt{NGLL} specified in the main constants
file \texttt{setup/constants.h}. The wave speed $v$ is determined based on your model's P- (or S-)
wave speed values.\newline

### 2022-11-30 doc/USER_MANUAL/05_running_the_solver.tex

If you know the earthquake source in strike/dip/rake format rather
than in \texttt{CMTSOLUTION} format, use the C code \texttt{SPECFEM3D\_GLOBE/utils/strike\_dip\_rake\_to\_CMTSOLUTION.c}
to convert it. The conversion formulas are given for instance in \citet{AkRi80}.
Note that the \citet{AkRi80} convention is slightly different from
the Harvard \texttt{CMTSOLUTION} convention (the sign of some components
is different). The C code outputs both.

Centroid latitude and longitude should be provided in geographical
coordinates. The code converts these coordinates to geocentric coordinates~\citep{DaTr98}.
Of course you may provide your own source representations by designing
your own \texttt{CMTSOLUTION} file. Just make sure that the resulting
file adheres to the Harvard CMT conventions (see Appendix~\ref{cha:Coordinates}).
Note that the first line in the \texttt{CMTSOLUTION} file is the Preliminary
Determination of Earthquakes (PDE) solution performed by the USGS
NEIC, which is used as a seed for the Harvard CMT inversion. The PDE
solution is based upon P waves and often gives the hypocenter of the
earthquake, i.e., the rupture initiation point, whereas the CMT solution
gives the `centroid location', which is the location with dominant
moment release. The PDE solution is not used by our software package
but must be present anyway in the first line of the file.

\label{To-simulate-a}To simulate a kinematic rupture, i.e., a finite-source
event, represented in terms of $N_{\mathrm{sources}}$ point sources,
provide a \texttt{CMTSOLUTION} file that has $N_{\mathrm{sources}}$
entries, one for each subevent (i.e., concatenate $N_{\mathrm{sources}}$
\texttt{CMTSOLUTION} files to a single \texttt{CMTSOLUTION} file).
At least one entry (not necessarily the first) must have a zero \texttt{time
shift}, and all the other entries must have non-negative \texttt{time
shift}. Each subevent can have its own half duration, latitude, longitude,
depth, and moment tensor (effectively, the local moment-density tensor).

Note that the zero in the synthetics does NOT represent the hypocentral
time or centroid time in general, but the timing of the \textit{center}
of the source triangle with zero \texttt{time shift} (Fig~\ref{fig:source_timing}).

Although it is convenient to think of each source as a triangle, in
the simulation they are actually Gaussians (as they have better frequency
characteristics). The relationship between the triangle and the gaussian
used is shown in Fig~\ref{fig:gauss.vs.triangle}. For finite fault
simulations it is usually not advisable to use a zero half duration
and convolve afterwards, since the half duration is generally fixed
by the finite fault model.

@@

Solver output is provided in the \texttt{OUTPUT\_FILES} directory
in the \texttt{output\_solver.txt} file. Output can be directed to
the screen instead by uncommenting a line in \texttt{setup/constants.h}:
\begin{verbatim}
! uncomment this to write messages to the screen
! integer, parameter :: IMAIN = ISTANDARD_OUTPUT
\end{verbatim}
On PC clusters the seismogram files are generally written to the local
disks (the path \texttt{LOCAL\_PATH} in the \texttt{DATA/Par\_file} and
need to be gathered at the end of the simulation.

While the solver is running, its progress may be tracked by monitoring
the `\texttt{\small timestamp{*}}' files in the \texttt{\small OUTPUT\_FILES/} directory. These tiny
files look something like this:
{\small
\begin{verbatim}
Time step #          10000
Time:     108.4890      seconds
Elapsed time in seconds =    1153.28696703911
Elapsed time in hh:mm:ss =     0 h 19 m 13 s
Mean elapsed time per time step in seconds =     0.115328696703911
Max norm displacement vector U in all slices (m) =     1.0789589E-02
\end{verbatim}
}
The \texttt{\small timestamp{*}} files provide the
\texttt{\small Mean elapsed time per time step in seconds}, which may be used
to assess performance on various machines (assuming you are the only
user on a node), as well as the
\texttt{\small Max norm displacement vector U in all slices~(m)}.
If something is wrong with the
model, the mesh, or the source, you will see the code become unstable
through exponentially growing values of the displacement and fluid
potential with time, and ultimately the run will be terminated by
the program. You can control the rate at which the timestamp files
are written based upon the parameter
\texttt{\small NTSTEP\_BETWEEN\_OUTPUT\_INFO}
in the \texttt{DATA/Par\_file}.

Having set the \texttt{DATA/Par\_file} parameters, and having provided
the \texttt{CMTSOLUTION} (or the \texttt{FORCESOLUTION}) and \texttt{STATIONS}
files, you are now ready to launch the solver! This is most easily
accomplished based upon the \texttt{go\_solver} script (See Chapter
\ref{cha:Scheduler} for information about running through a scheduler,
e.g., LSF). You may need to edit the last command at the end of the
script that invokes the \texttt{mpirun} command. The \texttt{runall}
script compiles and runs both \texttt{xgenerate\_databases} and \texttt{xspecfem3D}
in sequence. This is a safe approach that ensures using the correct
combination of distributed database output and solver input.

It is important to realize that the CPU and memory requirements of
the solver are closely tied to choices about attenuation (\texttt{ATTENUATION})
and the nature of the model (i.e., isotropic models are cheaper than
anisotropic models). We encourage you to run a variety of simulations
with various flags turned on or off to develop a sense for what is
involved.

@@

We have also added the ability to run several calculations (several earthquakes)
in an embarrassingly-parallel fashion from within the same run;
this can be useful when using a very large supercomputer to compute
many earthquakes in a catalog, in which case it can be better from
a batch job submission point of view to start fewer and much larger jobs,
each of them computing several earthquakes in parallel.
To turn that option on, set parameter \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS}
to a value greater than 1 in file \texttt{DATA/Par\_file}.

When that option is on, of course the number of processor cores used to start
the code in the batch system must be a multiple of \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS},
all the individual runs must use the same number of processor cores,
which as usual is \texttt{NPROC} in the input file \texttt{DATA/Par\_file},
and thus the total number of processor cores to request from the batch system
should be \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS $\times$ NPROC}.

>>>>

If you know the earthquake source in strike/dip/rake format rather
than in \texttt{CMTSOLUTION} format, use the C code \texttt{SPECFEM3D\_GLOBE/utils/strike\_dip\_rake\_to\_CMTSOLUTION.c}
to convert it. The conversion formulas are given for instance in \citet{AkRi80}.
Note that the \citet{AkRi80} convention is slightly different from
the Harvard \texttt{CMTSOLUTION} convention (the sign of some components
is different). The C code outputs both.\newline

Centroid latitude and longitude should be provided in geographical
coordinates. The code converts these coordinates to geocentric coordinates~\citep{DaTr98}.
Of course you may provide your own source representations by designing
your own \texttt{CMTSOLUTION} file. Just make sure that the resulting
file adheres to the Harvard CMT conventions (see Appendix~\ref{cha:Coordinates}).
Note that the first line in the \texttt{CMTSOLUTION} file is the Preliminary
Determination of Earthquakes (PDE) solution performed by the USGS
NEIC, which is used as a seed for the Harvard CMT inversion. The PDE
solution is based upon P waves and often gives the hypocenter of the
earthquake, i.e., the rupture initiation point, whereas the CMT solution
gives the `centroid location', which is the location with dominant
moment release. The PDE solution is not used by our software package
but must be present anyway in the first line of the file.\newline

\label{To-simulate-a}To simulate a kinematic rupture, i.e., a finite-source
event, represented in terms of $N_{\mathrm{sources}}$ point sources,
provide a \texttt{CMTSOLUTION} file that has $N_{\mathrm{sources}}$
entries, one for each subevent (i.e., concatenate $N_{\mathrm{sources}}$
\texttt{CMTSOLUTION} files to a single \texttt{CMTSOLUTION} file).
At least one entry (not necessarily the first) must have a zero \texttt{time
shift}, and all the other entries must have non-negative \texttt{time
shift}. Each subevent can have its own half duration, latitude, longitude,
depth, and moment tensor (effectively, the local moment-density tensor).\newline

Note that the zero in the synthetics does NOT represent the hypocentral
time or centroid time in general, but the timing of the \textit{center}
of the source triangle with zero \texttt{time shift} (Fig~\ref{fig:source_timing}).\newline

Although it is convenient to think of each source as a triangle, in
the simulation they are actually Gaussians (as they have better frequency
characteristics). The relationship between the triangle and the gaussian
used is shown in Fig~\ref{fig:gauss.vs.triangle}. For finite fault
simulations it is usually not advisable to use a zero half duration
and convolve afterwards, since the half duration is generally fixed
by the finite fault model.\newline

@@

Solver output is provided in the \texttt{OUTPUT\_FILES} directory
in the \texttt{output\_solver.txt} file. Output can be directed to
the screen instead by uncommenting a line in \texttt{setup/constants.h}:
\begin{verbatim}
! uncomment this to write messages to the screen
! integer, parameter :: IMAIN = ISTANDARD_OUTPUT
\end{verbatim}
On PC clusters the seismogram files are generally written to the local
disks (the path \texttt{LOCAL\_PATH} in the \texttt{DATA/Par\_file} and
need to be gathered at the end of the simulation.\newline

While the solver is running, its progress may be tracked by monitoring
the `\texttt{\small timestamp{*}}' files in the \texttt{\small OUTPUT\_FILES/} directory. These tiny
files look something like this:
{\small
\begin{verbatim}
Time step #          10000
Time:     108.4890      seconds
Elapsed time in seconds =    1153.28696703911
Elapsed time in hh:mm:ss =     0 h 19 m 13 s
Mean elapsed time per time step in seconds =     0.115328696703911
Max norm displacement vector U in all slices (m) =     1.0789589E-02
\end{verbatim}
}
The \texttt{\small timestamp{*}} files provide the
\texttt{\small Mean elapsed time per time step in seconds}, which may be used
to assess performance on various machines (assuming you are the only
user on a node), as well as the
\texttt{\small Max norm displacement vector U in all slices~(m)}.
If something is wrong with the
model, the mesh, or the source, you will see the code become unstable
through exponentially growing values of the displacement and fluid
potential with time, and ultimately the run will be terminated by
the program. You can control the rate at which the timestamp files
are written based upon the parameter
\texttt{\small NTSTEP\_BETWEEN\_OUTPUT\_INFO}
in the \texttt{DATA/Par\_file}.\newline

Having set the \texttt{DATA/Par\_file} parameters, and having provided
the \texttt{CMTSOLUTION} (or the \texttt{FORCESOLUTION}) and \texttt{STATIONS}
files, you are now ready to launch the solver! This is most easily
accomplished based upon the \texttt{go\_solver} script (See Chapter
\ref{cha:Scheduler} for information about running through a scheduler,
e.g., LSF). You may need to edit the last command at the end of the
script that invokes the \texttt{mpirun} command. The \texttt{runall}
script compiles and runs both \texttt{xgenerate\_databases} and \texttt{xspecfem3D}
in sequence. This is a safe approach that ensures using the correct
combination of distributed database output and solver input.\newline

It is important to realize that the CPU and memory requirements of
the solver are closely tied to choices about attenuation (\texttt{ATTENUATION})
and the nature of the model (i.e., isotropic models are cheaper than
anisotropic models). We encourage you to run a variety of simulations
with various flags turned on or off to develop a sense for what is
involved.\newline

@@

We have also added the ability to run several calculations (several earthquakes)
in an embarrassingly-parallel fashion from within the same run;
this can be useful when using a very large supercomputer to compute
many earthquakes in a catalog, in which case it can be better from
a batch job submission point of view to start fewer and much larger jobs,
each of them computing several earthquakes in parallel.
To turn that option on, set parameter \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS}
to a value greater than 1 in file \texttt{DATA/Par\_file}.\newline

When that option is on, of course the number of processor cores used to start
the code in the batch system must be a multiple of \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS},
all the individual runs must use the same number of processor cores,
which as usual is \texttt{NPROC} in the input file \texttt{DATA/Par\_file},
and thus the total number of processor cores to request from the batch system
should be \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS $\times$ NPROC}.\newline

### 2022-11-30 doc/USER_MANUAL/11_graphics.tex

You have also the option to visualize the distributed databases produced
by \texttt{xgenerate\_databases} using Paraview \urlwithparentheses{www.paraview.org}.
For this, you must set the flag \texttt{SAVE\_MESH\_FILES} to \texttt{.true.}
in the main parameter file \texttt{DATA/Par\_file} (see Chapter~\ref{cha:Main-Parameter}
for details). This will create VTK files for each single partition.
You can then use Paraview \urlwithparentheses{www.paraview.org}
to visualized these partitions.

@@

{\footnotesize
\begin{verbatim}
./bin/xcombine_vol_data 0 3 velocity_Z_it000400 ./OUTPUT_FILES/DATABASES_MPI ./OUTPUT_FILES 0
\end{verbatim}
}
Here, $0$ is the number of the first processor, $3$ the number of the last one, \texttt{velocity\_Z\_it000400} the name of the files we want to combine without the prefix \texttt{proc000000*\_}, \texttt{./OUTPUT\_FILES/DATABASES\_MPI} the directory where the files are located, \texttt{./OUTPUT\_FILES} the directory where the combined file will be stored, and $0$ is the parameter to create a low-resolution mesh file ($1$ for a high-resolution).

When compiling the code, you will get two executables related to this: xcombine\_vol\_data, and xcombine\_vol\_data\_vtk.
Use the executable that has the \_vtk extension if you want to directly create VTK files.
If you use the executable that does not have the \_vtk extension, then the output mesh file will have a name of the form \texttt{velocity\_Z\_it000400.mesh}.
You will then have to convert the \texttt{.mesh} file into the VTU (Unstructured grid file) format which can be viewed in ParaView.

@@

Notice that this Perl script uses a program \texttt{mesh2vtu} in the \texttt{utils/Visualization/Paraview/mesh2vtu} directory, which further
uses the VTK \urlwithparentheses{http://www.vtk.org} run-time library for its execution. Therefore, make sure you have them properly set
in the script according to your system.

@@

We will only discuss the case of one source-receiver pair, i.e., the
so-called banana-doughnut kernels. Although it is possible to collect
the kernel files from all slices on the front end, it usually takes
up too much storage space (at least tens of gigabytes). Since the
sensitivity kernels are the strongest along the source-receiver great
circle path, it is sufficient to collect only the slices that are
along or close to the great circle path.

>>>>

You have also the option to visualize the distributed databases produced
by \texttt{xgenerate\_databases} using Paraview \urlwithparentheses{www.paraview.org}.
For this, you must set the flag \texttt{SAVE\_MESH\_FILES} to \texttt{.true.}
in the main parameter file \texttt{DATA/Par\_file} (see Chapter~\ref{cha:Main-Parameter}
for details). This will create VTK files for each single partition.
You can then use Paraview \urlwithparentheses{www.paraview.org}
to visualized these partitions.\newline

@@

{\footnotesize
\begin{verbatim}
./bin/xcombine_vol_data 0 3 velocity_Z_it000400 ./OUTPUT_FILES/DATABASES_MPI ./OUTPUT_FILES 0
\end{verbatim}
}
Here, $0$ is the number of the first processor, $3$ the number of the last one, \texttt{velocity\_Z\_it000400} the name of the files we want to combine without the prefix \texttt{proc000000*\_}, \texttt{./OUTPUT\_FILES/DATABASES\_MPI} the directory where the files are located, \texttt{./OUTPUT\_FILES} the directory where the combined file will be stored, and $0$ is the parameter to create a low-resolution mesh file ($1$ for a high-resolution).\newline

When compiling the code, you will get two executables related to this: xcombine\_vol\_data, and xcombine\_vol\_data\_vtk.
Use the executable that has the \_vtk extension if you want to directly create VTK files.
If you use the executable that does not have the \_vtk extension, then the output mesh file will have a name of the form \texttt{velocity\_Z\_it000400.mesh}.
You will then have to convert the \texttt{.mesh} file into the VTU (Unstructured grid file) format which can be viewed in ParaView.\newline

@@

Notice that this Perl script uses a program \texttt{mesh2vtu} in the \texttt{utils/Visualization/Paraview/mesh2vtu} directory, which further
uses the VTK \urlwithparentheses{http://www.vtk.org} run-time library for its execution. Therefore, make sure you have them properly set
in the script according to your system.\newline

@@

We will only discuss the case of one source-receiver pair, i.e., the
so-called banana-doughnut kernels. Although it is possible to collect
the kernel files from all slices on the front end, it usually takes
up too much storage space (at least tens of gigabytes). Since the
sensitivity kernels are the strongest along the source-receiver great
circle path, it is sufficient to collect only the slices that are
along or close to the great circle path.\newline
